HydroPowerModels.jl: A Julia/JuMP Package for Hydrothermal Economic Dispatch Optimization

### 2019-07-07 paper/paper.tex

The simulate command returns a detailed dictionary of the execution. In order to plot those results returned by the simulate function, you may choose from a variety of methods, including the function ’plot\underline{\space}aggregated\underline{\space}results()’. This function receives the dictionary results and generates the most common aggregated variable plots, which best summarize simulations of a hydrothermal dispatch:

@@

Figures \ref{fig:plot_agg_result_thermal} to \ref{fig:plot_agg_result_inflow} show the output from the above command. As mentioned, the plots are of aggregated quantities, but the methods used to aggregate were chosen in order to help analysis. For example: The final nodal price is an average of nodal prices weighted by the contribution of local loads to the total demand; Reservoir volume was grouped weighted by the amount of energy that could be produced by the stored water (as was the inflow of water).

As expected the optimal dispatch of the simulations uses more hydro-generators, however it needs thermal-generators to met all demands without deficit.

On this hydro-dominated system, the uncertain inflow is a driving factor of optimal dispatch. As we can see in \ref{fig:plot_agg_result_inflow}, the inflow has a strong seasonality component, resulting the significant seasonality trait observable in the variables of the policy simulations \ref{fig:plot_agg_result_thermal}-\ref{fig:plot_agg_result_load},\ref{fig:plot_agg_result_hydrogen}-\ref{fig:plot_agg_result_vol},.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.55\linewidth]{fig/plot_agg_result_thermal.png}}
\label{fig:plot_agg_result_thermal}
\caption{Thermal Generation}
\end{figure}

>>>>

The simulate command returns a detailed dictionary of the execution. In order to plot those results returned by the simulate function, you may choose from a variety of methods, including the function \texttt{plot\_aggregate\_results()}. This function receives the dictionary results and generates the most common aggregated variable plots, which best summarize simulations of a hydrothermal dispatch:

@@

% Figures \ref{fig:plot_agg_result_thermal} to
Figures 2 to \ref{fig:plot_agg_result_inflow} show the output from the above command. As mentioned, the plots are of aggregated quantities, but the methods used to aggregate were chosen in order to help analysis. For example: The final nodal price is an average of nodal prices weighted by the contribution of local loads to the total demand; Reservoir volume was grouped weighted by the amount of energy that could be produced by the stored water (as was the inflow of water).

As expected the optimal dispatch of the simulations uses more hydro-generators, however it needs thermal-generators to met all demands without deficit. On this hydro-dominated system, the uncertain inflow is a driving factor of optimal dispatch. As we can see in Figure \ref{fig:plot_agg_result_inflow}, the inflow has a strong seasonality component, resulting the significant seasonality trait observable in the variables of the policy simulations.
%\ref{fig:plot_agg_result_thermal}
2-\ref{fig:plot_agg_result_load}, \ref{fig:plot_agg_result_hydrogen}-\ref{fig:plot_agg_result_vol}.

@@

% \begin{figure}[!ht]\label{fig:thermal}
% \centering
% \includegraphics[width=0.5\columnwidth]{fig/plot_agg_result_thermal.png}
% \caption{Aggregated quantity of thermal generation.}
% \end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=0.5\linewidth]{fig/plot_agg_result_thermal.png}}
\label{fig:plot_agg_result_thermal}
\caption{Thermal Generation}
\end{figure}
